APPM report - Draft

### 2022-10-13 paper_version/main.tex
polish until BCs

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage{natbib}
\bibliographystyle{apalike}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{subcaption}

@@

\title{APPM report - Draft}
\author{T.W. Yu, R. Fuchs, R. Hiptmair}

@@

\todobox{
    \begin{itemize}
        \item For the time being, the contents are just clipped from master thesis. They could be very chaotic.
        \item The figures are not added yet.
        \item For sure some parts need rewriting.
    \end{itemize}
}

@@

An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We start from their dimensionless model and extend the scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. This scheme turns out to be AP for $\lambda_D\to 0$ both in terms of structure and empirically in numerical test. Special care is necessary for the boundary conditions which must be valid in both regimes. Additionally, if the electromagnetic fields have to be modeled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.

\section{Plasma model}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations. The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.

\todo{A bit more on the physical background}.

After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasineutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.

In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure. The quasi-neutral model will be make clear by letting the rescalled Debye length $\lambda$ go to zero. Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed. Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.

@@

\subsection{The Maxwell-Euler System}
The Maxwell system is described by Maxwell's equations whose expression in SI units read
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous mediums in vacuum. We consider the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) serve as initial conditions. Faraday's law (\ref{equ:maxwell_faraday}) and Amp\`{e}re's law (\ref{equ:maxwell_ampere}) suffice.

In the Euler system, the motions of gas particles are accounted for through the \emph{Euler equations}. Specifically, we equip each species with one set of (compressible) Euler equations, taking into account the effect of electromagnetic fields as well as other processes like collisions and recombination. The generic expressions read
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. Note that the heat conduction is omitted in the energy equation. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms that include effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity, we would only consider ion-electron collision in this work. Under moderate assumptions, such collisions can be well modelled by friction terms, and we simply present the expressions without derivation (see \citep[][sec. 5.6.2]{chen2016}):
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which models the collision force that is applied on the electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 . Because of the conservation of momentum, the collision term experienced by ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$. For full details about the ionization and recombination, readers are referred to \cite{fuchs_2021}.

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems takes effect through the following relations that connect the fluid and electromagnetic quantities
\begin{equation*}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation*}

\subsection{Rescalling}
In the rescalling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into a dimensionless form. The magnitudes of the dimensionless numbers are indications of the magnitude of corresponding terms. In this part, the rescalling procedure mostly sticks to that of \cite{degond_2017}.

First, reference units for each quantity, e.g. the characteristic length and time scale, are prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest to the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity to the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity to the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy to the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field to the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass ratio to the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark}.&
\end{align*}
\footnotetext{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

Special treatment is needed for the collision term. One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}. Therefore, for the sake of simplicity, we decide to assume $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation\footnote{The reasonableness of this assumption is questionable.}.

@@

\vspace{10pt}
A small remark goes to the validity of assignment of electric potentials on $\Gamma_c^i$. Since the surface curl $\text{curl}_\gamma\mathbf{E} = \text{curl} \mathbf{E} \cdot \mathbf{n} = 0$, there exists a surface potential $\varphi$ such that the surface gradient $\nabla_\Gamma \varphi = \gamma_\tau \mathbf{E}$ where $\gamma_\tau $ is the tangential trace operator.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{a4paper,scale=0.8}
\usepackage[square,numbers]{natbib}
\bibliographystyle{abbrvnat}
\usepackage{tikz}
\usetikzlibrary{positioning, decorations.markings, arrows, intersections}
\usepackage{nicematrix}
\NiceMatrixOptions{cell-space-top-limit = 4pt}
\NiceMatrixOptions{cell-space-bottom-limit = 4pt}
\usepackage{tcolorbox}
\usepackage{subcaption}

\newtheorem*{remark}{Remark}

@@

\title{APPM report - Draft}
\author{T.W. Yu\footnote{SAM, ETH Z\"{u}rich}, R. Hiptmair\footnote{SAM, ETH Z\"{u}rich}, R. Fuchs\footnote{IET Institut für Energietechnik, OST}}

@@

@@

An asymptotic preserving scheme for single- and multi-fluid Euler-Maxwell system was proposed by \cite{degond_2012} for one spatial dimension. We start from their dimensionless model and extend the scheme to three dimensions. The key ingredients are (i) a discretization of Maxwell's equations based on primal and dual meshes in the spirit of discrete exterior calculus (DEC)/the finite integration technique (FIT), (ii) finite volume method (FVM) for the fluid equations on the dual mesh, and (iii) mixed implicit-explicit timestepping. This scheme turns out to be AP for $\lambda_D\to 0$ both in terms of structure and empirically in numerical test. Special care is necessary for the boundary conditions which must be valid in both regimes. Additionally, if the electromagnetic fields have to be modelled in an insulating region beyond the plasma domain, additional stabilization is necessary to accommodate Gauss's law.

\section{Introduction}
We consider a hydrodynamic multi-species plasma model, which boils down to the Maxwell-Euler system. As in \cite{degond_2012}, our focus is an \emph{asymptotic-preserving} (AP) discretization in the quasi-neutral limit $\lambda_D \rightarrow 0$, where $\lambda_D$ is the rescaled Debye length, see Section \ref{sec:rescaling} for the underlying scaling arguments and \cite{degond_2012,degond_2017} for a discussion of the importance of the AP property in plasma codes.

Our approach is inspired by \cite{degond_2012}, but goes beyond that work in various directions:
\begin{itemize}
    \item we supplement the Maxwell-Euler system by inter-species friction, see Section ?;
    \item we extend the spatially 1D scheme to three spatial dimensions;
    \item we propose an essential stabilization in non-conducting regions;
    \item we introduce suitable boundary conditions for the electromagnetic fields at a spatial truncateion boundary.
\end{itemize}

We stay close to \cite{degond_2012} in terms of discretization in time by semi-implicit time-stepping and by restricting to a cylindrical geometry shown in Fig. \ref{fig:domain_geometry}. We would like to remark that the mesh-based numerical scheme proposed in this paper can in principle be adapted to geometric situations much more general than that of Fig. \ref{fig:domain_geometry}. However, one may then encounter subtle problems in defining proper mesh duality as we do in Section ?. Thus, for the sake of simplicity of presentation we forgo geometric generality.

The content of this paper is organized as follows. In Section 2, we first give full details on the underlying equations of the Maxwell-Euler system and its rescaling procedure. Afterwards we introduce the ECE-type boundary conditions for our problem. A reformulation of the Maxwell equations in the insulating region is then presented. Section 3 is devoted to the discretization. \todo{outline}

\begin{figure}
    \centering
    \begin{tikzpicture}
    \coordinate (O1) at (0,0);
    \draw[violet] (O1) circle (1) node[blue] {Electrode};
    \fill[blue, opacity=0.2] (O1) circle (1);
    \draw[very thick] (O1) circle (1.5);
    \coordinate (O2) at (4.5,1);
    \draw[violet] (O2) circle (1);
    \node at (O2) {\textcolor{red}{Electrode}};
    \node at (barycentric cs:O1=1,O2=1) {Plasma}; 
    \fill[red, opacity=0.2] (O2) circle (1);
    \coordinate (S1) at ([shift={(-0.196,0.98)}]O1);
    \coordinate (S2) at ([shift={(-0.196,0.98)}]O2);
    \coordinate (P1) at ([shift={(0.196,-0.98)}]O1);
    \coordinate (P2) at ([shift={(0.196,-0.98)}]O2);
    \draw[violet] (S1) -- (S2);
    \draw[violet] (P1) -- (P2);
    \coordinate (SS1) at ([shift={({-0.196*1.5},{0.98*1.5})}]O1);
    \coordinate (SS2) at ([shift={({-0.196*1.5},{0.98*1.5})}]O2);
    \coordinate (PP1) at ([shift={({0.196*1.5},{-0.98*1.5})}]O1);
    \coordinate (PP2) at ([shift={({0.196*1.5},{-0.98*1.5})}]O2);
    \draw[very thick] (SS1) -- (SS2);
    \draw[very thick] (PP1) -- (PP2); 
    \draw[black, very thick] (SS2) arc (101.31:180+101.31:1.5);
    \draw[very thick] (PP2) arc (101.31-180:101.31:1.5);
    \draw[-to] (barycentric cs:SS1=1,SS2=1,S1=1,S2=1) to[out=90,in=0] ([shift={(-0.5,0.5)}]barycentric cs:SS1=1,SS2=1,S1=1,S2=1) node[left, gray] {Insulator};
    \begin{scope}[shift={(5.5,-1.4)}]
    \draw[blue, -to] (0,0) -- (0.65,0.12) node[right]{\small $z$};
    \draw[blue, -to] (0,0) -- (0,0.7) node[above]{\small $x$};
    \draw[blue, -to] (0,0) -- (0.7,0) node[below]{\small $y$};
    \end{scope}
    \end{tikzpicture}
\caption{The domain geometry}
\label{fig:domain_geometry}
\end{figure}

\section{Plasma model}
\begin{comment}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluid and described by hydrodynamic equations. The Maxwell equations are involved to describe their induction of and interaction with electromagnetic fields.

After rescalling all the variables with respect to the prescribed reference units, the Debye length $\lambda_D$, characterizing the charge screening ability of the plasma, would pop up and its zero limit, which is what we called \emph{quasi-neutral limit}, is of great interest, since the limit model largely simplifies the system and in many cases the accuracy of the assumption is satisfactory enough.

In this section, the multi-species Maxwell-Euler equations with collision term is introduced first, followed by detailed rescalling procedure. The quasi-neutral model will be make clear by letting the rescaled Debye length $\lambda$ go to zero. Afterwards, a set of boundary conditions are presented and its validity to both non-limit and limit model is discussed. Finally, we would like to present a reformulation of the system which would be crucial to the stability of the numerical scheme.
\end{comment}

@@

\subsection{The Maxwell-Euler System}
Under moderate assumptions, plasmas, which are gases composed of charged particles (and possibly neutral particles), can be treated as fluids governed by hydrodynamic equations. The Maxwell equations take charge of their interaction with electromagnetic fields. For more details on the fluid model of plasma, see \cite{chen2016, remi_2014}.

The Maxwell's equations in SI units read
\begin{subequations}
\begin{align}
    \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday} \\ 
    \partial_t \mathbf{D} - \nabla \times \mathbf{H} &= -\mathbf{J}, \label{equ:maxwell_ampere} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B}\\
    \nabla \cdot \mathbf{D} &= \rho, \label{equ:maxwell_gauss_D}
\end{align}
\end{subequations}
where the involved quantities are magnetic flux density $\mathbf{B}$, electric field intensity $\mathbf{E}$, electric induction $\mathbf{D}$, magnetic field intensity $\mathbf{H}$, electric current density $\mathbf{J}$ and electric charge density $\rho$. These equations are known as Faraday's law (\ref{equ:maxwell_faraday}), Amp\`{e}re's law (\ref{equ:maxwell_ampere}), Gauss's law for magnetism (\ref{equ:maxwell_gauss_B}) and Gauss's law for electric field (\ref{equ:maxwell_gauss_D}). For simplicity, we only consider isotropic and homogeneous media in vacuum. We consider the linear constitutive relations 
\begin{equation*}
    \mathbf{D} = \varepsilon_0 \mathbf{E}, \ \ \ \mathbf{B} = \mu_0\mathbf{H}, 
\end{equation*}
where $\varepsilon_0$ and $\mu_0$ are the vacuum permittivity and permeability of the medium. By definition of the electric current density $\mathbf{J}$ and electric charge density $\rho$, they are supposed to satisfy the continuity equation
\begin{equation} \label{equ:charge_continuity}
    \partial_t\rho + \nabla \cdot \mathbf{J} = 0.
\end{equation}
Besides, on taking the divergence of equations (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) together with the relation (\ref{equ:charge_continuity}), it is possible to verify that Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are consequences of (\ref{equ:maxwell_faraday}) and (\ref{equ:maxwell_ampere}) provided that (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) are satisfied at the initial time. In other words, Gauss's laws (\ref{equ:maxwell_gauss_B}) (\ref{equ:maxwell_gauss_D}) can be thought of as initial conditions.

Each species in plasmas are treated as a compressible flow and assocated to one set of Euler equations that includes electromagnetic forces as well as other processes, e.g. collisions and recombination. The generic expressions are
\begin{align} \label{equ:euler_}
    \partial_t
    \begin{bmatrix}
    n_* \\
    m_*n_* \mathbf{u}_* \\
    m_*n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    n_* \mathbf{u}_* \\
    m_*n_* \mathbf{u}_* \otimes \mathbf{u}_* + p_*\mathbb{I} \\
    m_*n_* h_* \mathbf{u}_*
    \end{bmatrix}
    =
    \begin{bmatrix}
    0 \\
    q_*n_*(\mathbf{E} + \mathbf{u}_* \times \mathbf{B}) \\
    \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix}
    +
    \begin{bmatrix}
    \Gamma_* \\
    \mathbf{R}_* \\
    Q_*
    \end{bmatrix}.
\end{align}
The subscript $*$ represents the indices for different species, and by convention we assign $* = e$ to electrons, $* = i$ to ions, and $* = n$ to neutral atoms. The involved fluid quantities are: number density $n_*$, particle mass $m_*$,  charge number $q_*$, velocity $\mathbf{u}_*$, pressure $p_*$, specific total energy $e_* := \frac{1}{2}|\mathbf{u}_*|^2 + \frac{p_*}{m_*n_*(\gamma - 1)}$, specific total enthalpy $h_* := e_* + \frac{p_*}{m_*n_*}$ and current density $\mathbf{J}_* := q_*n_*\mathbf{u}_*$. All the species are assumed ideal gases with heat capacity ratio $\gamma=5/3$ for monatomic gases. The left-hand side of the equations describes the convection of plasma fluids. The first term at the right-hand side denotes Lorentz force in the momentum equation and Joule heating in the energy equation. $\Gamma_*, \mathbf{R}_*, Q_*$ are generic terms due to effects of inter-species collision, ionization, recombination, etc.

For the sake of simplicity for presentation, we only consider ion-electron collision in this work, but extension to more species is straightforward. Under moderate assumptions, such collisions can be well modelled by frictions, and we simply present the expressions without derivation (see \citep[][sec. 5.6.2]{chen2016}):
\begin{equation} \label{equ:collision}
    \mathbf{R}_{e}^{\text{coll}} = \frac{\pi Ze^4m_e^{1/2}}{(4\pi\varepsilon_0)^2(k_BT_e)^{3/2}}\text{ln}\Lambda n_en_i(\mathbf{u}_i - \mathbf{u}_e) = - \mathbf{R}_{i}^{\text{coll}},  
\end{equation}
which models the collision force that is applied on the electrons. ln$\Lambda$ is called the \emph{Coulomb logarithm}, which typically takes a numerical value of order 10–20 . Because of the conservation of momentum, the collision term for ions $\mathbf{R}_{i}^{\text{coll}}$ is nothing but the negation of $\mathbf{R}_{e}^{\text{coll}}$. In this work, the other effects, e.g. ionization and recombination, are not considered. For full details about the modeling of these physical processes, readers are referred to \cite{fuchs_2021}.

Combination of the two sets of equations (\ref{equ:maxwell_faraday}) to (\ref{equ:maxwell_gauss_D}) and (\ref{equ:euler_}) leads to the governing equations for a multi-species plasma model. The coupling of the two subsystems is due to the following relations that connect the fluid and electromagnetic quantities
\begin{equation*}
    \rho = \sum_* q_*n_*, \ \ \  \mathbf{J} = \sum_* q_*n_*\mathbf{u}_*. 
\end{equation*}

\subsection{Rescaling} \label{sec:rescaling}
In the rescaling, the variables in the equations are taken as the ratio of their original quantities and reference units, which transforms the system into dimensionless form. In this part, the rescaling procedure mostly follows that of \cite{degond_2017}.

First, reference units for each quantity, e.g. the characteristic length and time scale, are prescribed. We define $\overline{x}$ and $\overline{t}$ as space and time scale of interest, by which the reference velocity $\overline{v}$ is defined as $\overline{x}/\overline{t}$. The typical magnitudes of electromagnetic fields are $\overline{E}$ and $\overline{B}$. The typical magnitudes of fluid quantities are denoted by $\overline{u}$ for plasma drift velocity, $\overline{n}$ for plasma number density, $\overline{T}$ for plasma temperature. On top of that, the typical pressure is set $\overline{n}k_B\overline{T}$ with $k_B$ being the Boltzmann constant; the typical value for the specific total energy and enthalpy is set $\overline{u}^2$. Together with the physical parameters, namely, permittivity $\varepsilon_0$, permeability $\mu_0$, light speed $c^2 = (\varepsilon_0\mu_0)^{-1}$, Boltzmann constant $k_B$, the elementary charge $e$, and ion mass $m_i$, the following dimensionless parameters are induced,
\begin{align*} 
    \xi &:= \frac{\overline{v}}{c} \text{ the velocity of interest \emph{w.r.t.}\footnotemark[1] the light speed}, &\\
    \zeta &:= \frac{\overline{u}}{\overline{v}} \text{ the plasma velocity \emph{w.r.t.} the speed of interest}, &\\
    M &:= \frac{\overline{u}}{v_{th,i}} \text{ the plasma drift velocity \emph{w.r.t.} the thermal speed of ions, where } v_{th,i} := \left(\frac{k_B \overline{T}}{m_i}\right)^{1/2}, &\\
    \eta &:= \frac{e\overline{E}\overline{x}}{m_i\overline{u}^2} \text{ the electric energy \emph{w.r.t.} the kinetic energy of ions}, &\\
    \beta &:= \frac{\overline{v}\overline{B}}{\overline{E}} \text{ the induced electric field \emph{w.r.t.} the total electric field}, &\\
    \lambda &:= \frac{\lambda_D}{\overline{x}} \text{ the dimensionless Debye length, where }\lambda_D := \left(\frac{\varepsilon_0k_B\overline{T}}{e^2\overline{n}}\right)^{1/2}, &\\
    \varepsilon_*^2 &:= \frac{m_*}{m_i} \text{ the species mass \emph{w.r.t.} the ion mass},\ \  * \in \{i,e,n,\cdots\}, &\\
    g &:= \frac{1}{\overline{n}\lambda_D^3} \text{ the plasma parameter\footnotemark[2]}.&
\end{align*}
\footnotetext[1]{Abbreviation of \emph{with respect to}.}
\footnotetext[2]{It is basically the reciprocal of the number of particles per Debye sphere, see \cite[][sec. 1.1]{gibbon2020}. Classical plasma theory assumes $g \ll 1$.}

By abuse of notation, the dimensionless quantities have the same symbol with their original ones without incurring any ambiguity. For the sake of simplicity, we only consider the collision terms, namely $\Gamma_* = 0, \mathbf{R}_* = \mathbf{R}_*^\text{coll}, Q_* = Q_*^\text{coll}$ in (\ref{equ:euler_}), while neglecting other effects. The rescaled Euler-Maxwell system reads
\begin{subequations}
\begin{align}
    \beta \partial_t \mathbf{B} + \nabla \times \mathbf{E} &= 0, \label{equ:maxwell_faraday_rescalling} \\ 
    \lambda^2 \partial_t \mathbf{E} - \frac{\beta \lambda^2}{\xi^2}\nabla \times \mathbf{B} &= - \frac{\zeta}{\eta M^2}\mathbf{J}, \label{equ:maxwell_ampere_rescalling} \\
    \nabla \cdot \mathbf{B} &= 0,  \label{equ:maxwell_gauss_B_rescalling}\\
    \lambda^2 \eta M^2 \nabla \cdot \mathbf{E} &= \rho, \label{equ:maxwell_gauss_D_rescalling} \\
    \partial_t
    \begin{bmatrix}
    n_* \\
    n_* \mathbf{u}_* \\
    n_* e_*
    \end{bmatrix}
    + \nabla \cdot
    \begin{bmatrix}
    \zeta n_* \mathbf{u}_* \\
    \zeta n_* \mathbf{u}_* \otimes \mathbf{u}_* + \zeta M^{-2} \varepsilon_*^{-2} p_*\mathbb{I} \\
    \zeta n_* h_* \mathbf{u}_*
    \end{bmatrix}
    &=
    \begin{bmatrix}
    0 \\
    \eta \zeta \varepsilon_*^{-2} q_* n_*\mathbf{E} + \eta \zeta^2 \beta \varepsilon_*^{-2} q_* n_* \mathbf{u}_* \times \mathbf{B} \\
    \zeta \eta \varepsilon_*^{-2} \mathbf{J}_* \cdot \mathbf{E}
    \end{bmatrix} +
    \begin{bmatrix}
    0 \\
    \varepsilon_*^{-2}\mathbf{R}_*^{\text{coll}} \\
    \varepsilon_*^{-2}Q_*^{\text{coll}} \\
    \end{bmatrix}, \label{equ:euler_rescalling}
\end{align}
\end{subequations}
where the equation of state becomes $e_* = \frac{1}{2}|\mathbf{u_*}|^2 + M^{-2}\frac{p_*}{\epsilon^2_* n_* (\gamma - 1)}$ and $h_* = e_* + M^{-2}\frac{p_*}{\epsilon^2_* n_*}$. For a fully-ionized gas, we have the original expression of $\mathbf{R}_*^{\text{coll}}$ in (\ref{equ:collision}), and its rescaled expression becomes
\begin{equation*}
    \mathbf{R}_i^{\text{coll}} = \frac{Z\text{ln}\Lambda}{16\pi}g\lambda^{-1}M^{-1}\varepsilon_en_en_i(\mathbf{u}_i - \mathbf{u}_e). 
\end{equation*}

@@

Special treatment is needed for the collision term. One would notice the inverse proportionality to $\lambda$, which would introduce a singular perturbation to the Euler system as $\lambda \rightarrow 0$. However, the validity of such a collision model is doubtful when $\lambda \rightarrow 0$. From the physical viewpoint, the shielding effect characterized by Debye length $\lambda$ makes the impact parameter no larger than $\lambda$. The $\lambda \rightarrow 0$ limit implies that the collisions happen in the atomic length scale, in which quantum-mechanical effects must be taken into effect \citep{frank_1972}. Therefore, for the sake of simplicity, we eliminate the perturbation parameter in the friction term by assuming $g \sim \lambda$ and keep the prefactor of collision term constant $\alpha^{\text{coll}}$ throughout the simulation.

\begin{remark}
    It is also of research interest when there is an asymptotic parameter at the denominator of the friction term. Such problem is called relaxation limit, see \cite{peng_2011, wasiolek_2016, Li_2021, Chen_2000}.
\end{remark}

@@

\vspace{10pt}
